BivData Setup

### 2020-02-11 src/BivData_Setup.Rmd
removed the empty hand foci lines from a mouse table loop

@@

mouse.level.BivData_table <- ddply(.data=Curated_BivData, 
                       .(mouse),
                       summarize,

@@

                       Nbiv = length(Obj.ID), #if there are na's below -- it breaks
                       tot.biv = length(Obj.ID),

@@

>>>>

- Fix the hand.foci.count ==2, 5jan19_27oct18_SKIVE_m2_sp1_3.2_rev_13

- Fix all the hand.foci == 4, which don't have the right number of positions

@@

#remove bivalent entries without hand foci count values

cleanCurated_BivData <-  Curated_BivData  %>%  filter(hand.foci.count  == 0 | hand.foci.count  == 1 |
                                      hand.foci.count  == 2 | hand.foci.count  == 3 | hand.foci.count  == 4 )

mouse.level.BivData_table <- ddply(.data=cleanCurated_BivData, 
                       .(mouse),
                       summarize,

@@

                       Nbiv = length(Obj.ID), #if there are na's below -- it breaks

                      tot.biv = length( !is.na(hand.foci.count) ),

@@

mouse.level.BivData_table$Rec.group <- ifelse(grepl("PWD male", mouse.level.BivData_table$category), 1, 
                              ifelse(grepl("MSM male", mouse.level.BivData_table$category), 1,
                                 ifelse(grepl("SKIVE male", mouse.level.BivData_table$category), 1, 0)))
```
